---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

# Step 1

# Step 2

Yes, there is a variable of special interest. \
This main variable is called: **"Sales Price"**.\

# Step 3

# Step 4

## Grace's Work

## Kyle's Work
I'm gonna look at the relationship between *Sales Price* and **Bedrooms**.\

```{r}
library(ggplot2)
library(dplyr)
bedrooms <- ames["Bedrooms"] |> filter(!is.na(Bedrooms))

bedrooms |> range()
bedrooms |> ggplot(aes(x=factor(Bedrooms))) + geom_bar(fill="skyblue") + geom_text(stat="count", aes(label=after_stat(count)), vjust=-.3) + labs(title="Bedroom Counts", x="Bedroom Count", y="Property Count")
```
The range for *bedrooms* in the *Ames* data set if **0** to **10**. Most houses have between 2 and 5 bedrooms,

```{r}
filteredAmes <- ames |> filter(!is.na(Bedrooms)) |> filter(!is.na(`Sale Price`)) |> filter(`Sale Price` != 0)
filteredAmes |> filter(`Sale Price` <= 1000000) |> ggplot(aes(x=factor(Bedrooms), y=`Sale Price`)) + geom_point(size=1) + labs(title="Bedrooms vs Sale Price <= $1,000,000", x="Bedroom Count", y="Sale Price")
```
```{r}
filteredAmes |> filter(`Sale Price` > 1000000) |> ggplot(aes(x=factor(Bedrooms), y=`Sale Price`)) + geom_point(size=1) +  labs(title="Bedrooms vs Sale Price > $1,000,000", x="Bedroom Count", y="Sale Price")
```

I had to separate the properties that sold for *> \$1,000,000* since they heavily skewed the graph to where the majority of the points were not visible. I'd say those properties were definite oddities, as they followed no pattern. As for the ones *<= \$1,000,000*, there is a slight pattern, where more bedrooms lead to higher sale price. However, there are many outliers, like the property with 0 bedrooms for ~\$740,000.
<br>
## Owen's Work

## Shiva's Work

## Olivia's Work
