---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.


# Step 1
There are 16 variables in this dataset, \
1. Parcel ID: character, unique ID for each property. \
2. Address: character, stores the address for individual property. \
3. Style: factor, type of house style(1 story, 2 story, etc.). \
4. Occupancy: factor, Says the type of occupancy (owner occupied, single family, etc.). \
5. Sale Date: Date, Date when the property was sold. \
6. Sale Price: numeric, Price the property was sold for, typically tens of thousands to several hundred thousand dollars. \
7. Multi Sale: character, Indicates if the property was sold multiple times. \
8. YearBuilt: numeric, year the house was built, usually between 1900 and recent years. \
9. Acres: numeric, Lot size of the property in acres, usually small values (0.05 – 1 acre for most homes). \
10. TotalLivingArea (sf): numeric, Total living area of the house in square feet, usually between ~500 and 4000 square feet. \
11. Bedrooms: numeric, number of bedrooms in the house, typically between 1 and 6. \
12. FinishedBsmtArea (sf): numeric, Finished basement area in square feet. \
13. LotArea(sf): numeric, Total lot size in square feet. \
14. AC: character, Whether the house has air conditioning (Yes/No). \
15. FirePlace: character, Whether the house has a fireplace. \
16. Neighborhood: factor, Neighborhood in Ames where the house is located. \

# Step 2

Yes, there is a variable of special interest. \
This main variable is called: **"Sales Price"**.\

# Step 3

# Step 4

## Grace's Work

## Kyle's Work
I'm gonna look at the relationship between *Sales Price* and **Bedrooms**.\

```{r}
library(ggplot2)
library(dplyr)
library(classdata)
data(ames)
bedrooms <- ames["Bedrooms"] |> filter(!is.na(Bedrooms))

bedrooms |> range()
bedroomsPlot <- bedrooms |> ggplot(aes(x=factor(Bedrooms))) + geom_bar(fill="skyblue") + geom_text(stat="count", aes(label=after_stat(count)), vjust=-.3) + labs(title="Bedroom Counts", x="Bedroom Count", y="Property Count")
bedroomsPlot
```
The range for *bedrooms* in the *Ames* data set if **0** to **10**. Most houses have between 2 and 5 bedrooms,

```{r}
filteredAmes <- ames |> filter(!is.na(Bedrooms)) |> filter(!is.na(`Sale Price`)) |> filter(`Sale Price` != 0)
subMilPropPlot <- filteredAmes |> filter(`Sale Price` <= 1000000) |> ggplot(aes(x=factor(Bedrooms), y=`Sale Price`)) + geom_point(size=1) + labs(title="Bedrooms vs Sale Price <= $1,000,000", x="Bedroom Count", y="Sale Price")
subMilPropPlot
```
```{r}
supMilPropPlot <- filteredAmes |> filter(`Sale Price` > 1000000) |> ggplot(aes(x=factor(Bedrooms), y=`Sale Price`)) + geom_point(size=1) +  labs(title="Bedrooms vs Sale Price > $1,000,000", x="Bedroom Count", y="Sale Price")
supMilPropPlot
```

\
I had to separate the properties that sold for *> \$1,000,000* since they heavily skewed the graph to where the majority of the points were not visible. I'd say those properties were definite oddities, as they followed no pattern. As for the ones *<= \$1,000,000*, there is a slight pattern, where more bedrooms lead to higher sale price. However, there are many outliers, like the property with 0 bedrooms for ~\$740,000.
<br>
## Owen's Work

## Shiva's Work
```{r}
library(classdata)
library(ggplot2)

data(ames)

ggplot(ames, aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) +
  geom_point(alpha = 0.5) +
  labs(
    title = "Sale Price vs Total Living Area",
    x = "Total Living Area (sq ft)",
    y = "Sale Price ($)"
  )
``` 

For this investigation, I explored the relationship between Sale Price and Total Living Area (sq ft) using a scatterplot. Most houses have living areas between about 500 and 4000 square feet, and their sale prices vary within a similar range. The plot does not show a very clear increasing pattern because several extremely high sale price values appear far above the rest of the data, which stretch the scale of the graph. These points are likely outliers or unusual luxury properties. Aside from these outliers, most houses cluster near the bottom of the plot, suggesting that other factors besides living area may also influence sale price.


## Olivia's Work

