---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

# Step 1

# Step 2

Yes, there is a variable of special interest. \
This main variable is called: **"Sales Price"**.\

# Step 3

The The lowest price is 0 and the highest is 20500000 making the range 20500000

```{r}
library(classdata)
data(ames)
hist(ames$`Sale Price`)
    
```

The histogram of sale price shows the majority of homes near zero dollars. This is because the data set shows a large amount of homes costing nothing. The histogram also shows a few houses that cost around 15 million dollars and 20 million dollars. 
It is odd that most of the price variables are zero in the data set. This could be due many reasons. For example, the price of the house could be private, there could have been an error populating the data, or an error in the data set itself. 



# Step 4

## Grace's Work

## Kyle's Work

## Owen's Work

## Shiva's Work

## Olivia's Work
